
\textbf{Instructions.}
\begin{itemize}
\item
   Homework is due \textbf{\duedate}; 
   no late homework accepted.

    \item
    Everyone must submit individually at Gradescope under  \hw{} and, if there is an autograder component, \hwc{}.

    \item
    The ``written'' submission at  \hw{} \textbf{must be typed}, and submitted in
    any format Gradescope accepts (to be safe, submit a PDF).  You may use \LaTeX, markdown,
    google docs, MS word, whatever you like; but it must be typed!
    \textbf{We reserve the right to deduct points for handwritten or otherwise illegible submissions.}

    \item
    When submitting at \hw{}, Gradescope will ask you to mark out boxes
    around each of your answers; please do this precisely! This includes, for example,
    plots generated in coding questions. Refer to the outline on Gradescope's \hw{}.

    \item
    Please make sure your NetID is clear and large on the first page of the homework.

    \item
    Your solution \textbf{must} be written in your own words.
    Please see the course webpage for full academic integrity information.
    Briefly, you may have high-level discussions with at most 3 classmates,
    whose NetIDs you should place on the first page of your solutions,
    and you should cite any external reference you use; despite all this,
    your solution must be written in your own words.

    \item
    We reserve the right to reduce the auto-graded score for \hwc{}
    if we detect funny business (e.g., rather than implementing an algorithm,
    you keep re-submitting the assignment to the auto-grader, eventually completing
    a binary search for the answers).

    \item
    There are \textbf{no regrade requests} on \hwc{} which is the code auto-grader;
    however, you can re-submit and re-grade as many times as you like before the deadline!
    Start early and report any issues on Campuswire.

    \item 
    Only submit \texttt{\hw{}.py} to the Gradescope \texttt{\hwc{}} assignment. 
    Do not submit any other files.

    \item
    Methods and functions in the template and utility code include
    docstrings describing the inputs and outputs.  The autograder
    relies on correct implementations of these methods.  Follow the
    docstrings to avoid failing tests.

    \item 
    Students are \textbf{permitted} to use LLMs, such as ChatGPT or Copilot, to streamline
    the completion of homework. However, students are required to disclose where and how LLMs
    were used, as well as provide references for any external resources used. 
\end{itemize}
